Online resolving assembly graph by ONT long reads data

### 2019-06-17 paper.tex
following flye

Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$ 
The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.

The log ratio of the density functions is
$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$

The metric we used is the distance defined as
$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$

@@

$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
The above function and be rewritten as:
$$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
and then being minimized by using Newton or gradient method.
\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
\end{itemize}
The calibration is iterative until no further improvements are made or a threshold loop count is reached.
\subsection*{Multiplicity estimation}
Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variances of coverage values. 
For that reason, they are only used as augmented information to calculate candidate paths' score in the next step.

>>>>

%%%Move to Supplementary
%Assume there are 2 Poisson distributions $P_1$ and $P_2$ with density functions $$p_1(x,\lambda_1)=\frac{e^{-\lambda_1}\lambda_1^x}{\Gamma(x+1)}$$ and $$p_2(x,\lambda_2)=\frac{e^{-\lambda_2}\lambda_2^x}{\Gamma(x+1)}$$ 
%The Kullback-Leibner divergence from $P_2$ to $P_1$ is defined as:
%$$D_{KL}(P_1||P_2)=\int_{-\infty}^{\infty} p_1(x)\log{\frac{p_1(x)}{p_2(x)}} dx$$
%or in other words,  it is the expectation of the logarithmic difference between the probabilities $P_1$ and $P_2$, where the expectation is taken with regard to $P_1$.
%
%The log ratio of the density functions is
%$$\log{\frac{p_1(x)}{p_2(x)}}=x\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
%take expectation of this expression with regard to $P_1$ with mean $\lambda_1$ we have
%$$D_{KL}(P_1||P_2)=\lambda_1\log{\frac{\lambda_1}{\lambda_2}}+\lambda_2-\lambda_1$$
%
%The metric we used is the distance defined as
%$$D(P_1,P_2)=\frac{D_{KL}(P_1||P_2)+D_{KL}(P_2||P_1)}{2}=\frac{1}{2}(\lambda_1-\lambda_2)(\log{\lambda_1}-\log{\lambda_2})$$

@@

$\sum{e^{+}_{i}}$ and $\sum{e^{-}_{i}}$ indicates sum of the values of incoming and outgoing edges from $i$ respectively. 
The above function and be rewritten as:
$$f(x)=\frac{1}{2}x^TQx + b^Tx + r$$
and then being minimized by using gradient-based method.
\item[2.] Update nodes' coverage based on itself and its neighbor edges' measures.
\end{itemize}
The calibration is iterative until no further improvements are made or a threshold loop count is reached.
\subsection*{Multiplicity estimation}
Based on the coverage values of all the edges and the graph's topology, we induce the copy numbers of every significant nodes (long contigs) in the final paths.
For each node, this could be done by investigating its adjacent edges and answering the questions of how many times it should be visited, from which abundance groups.
Multiplicities of insignificant nodes (of sequences with length less than $1,000$ bp) can be estimated in the same way but usually with less confident due to more complicated connections and greater variances of coverage values. 
For that reason, they are only used as augmented information to calculate candidate paths' score in the next step.
